Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2015-07-07 main/LMCS.tex
intro to "parity"

@@

Here, we will introduce a similar necessary condition for the equivalence of two proof nets. We shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, and we shall find that the parity of equivalent linkings is always even.

>>>>

%\end{document}

@@

Here, we will introduce a similar necessary condition for the equivalence of two proof nets. Consider the example of the identity and twist maps on $\bot\tn\bot$, below. The two maps are semantically distinct; hence they are often given as a minimal example showing the necessity of having jumps in proof nets.
\[
	\twistid0 \qquad\qquad \twistid1
\]
In this case, it is easily seen that neither jump can be rewired, and that the two nets are thus inequivalent; to change from one net to the other, two jumps would need to be rewired simultaneously. This prompts the question of what would happen in a larger net: would a complicated series of rewirings be able to exchange two jumps configured like those of the above nets? Or phrased semantically: are there maps that equalise the identity and twist on $\bot\tn\bot$ in the free $*$-autonomous category?

It turns out that this is not the case. Most provable sequents have at least two equivalence classes of proofs, such that for each proof in one class there is a corresponding proof, equal up to the exchange of two jumps, in the other. An example of this is Figure~\ref{fig:_*_,1,1,1,_*_}.

We will capture this idea as follows: we shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, which may be \emph{even} or \emph{odd}, and we shall find that the parity of equivalent linkings is always even.
